```{r}
# Load the necessary libraries
library(arrow)
library(dplyr)

# Correct the URL if necessary to remove spaces or encode them
url <- "https://intro-datascience.s3.us-east-2.amazonaws.com/SC-data/static_house_info.parquet"

# Read the Parquet file directly from the URL
static_house_data <- read_parquet(url)

# View the first few rows of the dataframe
head(static_house_data)

```

```{r}
# Filter data for county G4500410 and select specified columns
filtered_data <- static_house_data %>%
  filter(in.county == "G4500410") %>%
  select(
    bldg_id, in.sqft, in.bedrooms, in.geometry_stories,
    in.hvac_cooling_type, in.hvac_heating_type, in.hvac_heating_efficiency, 
    in.hvac_cooling_efficiency, in.hvac_has_ducts,in.county, in.occupants
  )

head(filtered_data)

colnames(filtered_data)

file_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Static_House_data/house_data_filtered.csv"

# Save the filtered dataframe as a CSV file
write.csv(filtered_data, file_path, row.names = FALSE)
```

```{r}
# Load the necessary libraries
library(arrow)
library(dplyr)
library(readr)
library(tidyr)

# Read the Parquet file directly from the URL
weather_data <- read_csv("https://intro-datascience.s3.us-east-2.amazonaws.com/SC-data/weather/2023-weather-data/G4500410.csv")

# View the first few rows of the dataframe
head(weather_data)

colnames(weather_data)

file_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Weather/weather_data.csv"

# Save the filtered dataframe as a CSV file
write.csv(weather_data, file_path, row.names = FALSE)
```

```{r}
# Load necessary libraries
library(arrow)
library(dplyr)
library(readr)
library(purrr)
library(lubridate)

# Set the path for the house data and read it
house_data_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Static_House_data/house_data_filtered.csv"
house_data <- read_csv(house_data_path)

# Define the function to load, filter, and augment energy data for a given building ID
load_and_filter_energy <- function(bldg_id) {
  file_url <- paste0("https://intro-datascience.s3.us-east-2.amazonaws.com/SC-data/2023-houseData/", bldg_id, ".parquet")
  energy_data <- arrow::read_parquet(file_url)
  
  # Convert time column to Date/Time class
  energy_data$time <- ymd_hms(energy_data$time)
  
  # Filter data from April to July
  energy_data <- energy_data %>%
    filter(month(time) >= 4 & month(time) <= 7)

  # Add bldg_id column
  energy_data$bldg_id <- bldg_id
  
  return(energy_data)
}

# Apply the function to each building ID, combining the results into one dataframe
combined_energy_data <- house_data$bldg_id %>%
  map_df(~load_and_filter_energy(.))

colnames(energy_data)

# Define the file path for saving the combined energy data
save_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Energy/energy_data.csv"

# Save the combined dataframe as a CSV file
write_csv(combined_energy_data, save_path, col_names = TRUE)

# Print a message upon successful completion
print("Energy data has been successfully saved.")

```

```{r}
library(dplyr)
library(readr)

# Load combined energy data
energy_data_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Energy/energy_data.csv"
energy_data <- read_csv(energy_data_path)

# Summarize energy consumption by category and add Heating and Cooling
energy_data_summarized <- energy_data %>%
  mutate(
    electricity = rowSums(select(., contains("electricity")), na.rm = TRUE),
    fuel = rowSums(select(., contains("fuel_oil")), na.rm = TRUE),
    natural_gas = rowSums(select(., contains("natural_gas")), na.rm = TRUE),
    propane = rowSums(select(., contains("propane")), na.rm = TRUE),
    Heating = rowSums(select(., matches("heating|hot_water|pool_heater|hot_tub_heater")), na.rm = TRUE),
    Cooling = rowSums(select(., matches("cooling|ceiling_fan")), na.rm = TRUE)
  ) %>%
  select(time, bldg_id, electricity, fuel, natural_gas, propane, Heating, Cooling) %>%
  group_by(time, bldg_id) %>%
  summarise(
    electricity = sum(electricity, na.rm = TRUE),
    fuel = sum(fuel, na.rm = TRUE),
    natural_gas = sum(natural_gas, na.rm = TRUE),
    propane = sum(propane, na.rm = TRUE),
    Heating = sum(Heating, na.rm = TRUE),
    Cooling = sum(Cooling, na.rm = TRUE),
    total_energy = electricity + fuel + natural_gas + propane
  )

colnames(energy_data_summarized)
# Save the summarized data
write_csv(energy_data_summarized, "C:/Users/puroh/OneDrive/Documents/IDS/Energy/energy_data_final.csv")

# Print a confirmation message
print("Summarized energy data has been successfully saved with additional Heating and Cooling aggregates.")
```

```{r}
# Load the necessary libraries
library(dplyr)
library(readr)
library(lubridate)

# Read the CSV file directly from the URL
weather_data <- read_csv("https://intro-datascience.s3.us-east-2.amazonaws.com/SC-data/weather/2023-weather-data/G4500410.csv")

# Convert date_time column to Date/Time class
weather_data$date_time <- ymd_hms(weather_data$date_time)

# Filter the data for the months of April to July
filtered_weather_data <- weather_data %>% 
  filter(month(date_time) >= 4 & month(date_time) <= 7)

# Rename the column 'date_time' to 'time'
filtered_weather_data <- filtered_weather_data %>%
  rename(time = date_time)

# View the first few rows of the dataframe
head(filtered_weather_data)

# Define the file path (Adjust the file path as necessary for your system)
file_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Weather/weather_data_filtered.csv"

# Save the filtered dataframe as a CSV file
write_csv(filtered_weather_data, file_path, col_names = TRUE)

# Print a message upon successful completion
print("Filtered weather data has been successfully saved.")

```

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(tidyr)

# Set the working directory to where your dataset is located
setwd("C:/Users/puroh/OneDrive/Documents/IDS/Static_House_data")

# Read the dataset
house_data <- read.csv("house_data_filtered.csv")

# View the structure of the dataset
str(house_data)
summary(house_data)

# Histogram of Square Footage
ggplot(house_data, aes(x = in.sqft)) +
  geom_histogram(bins = 30, fill = "cornflowerblue") +
  labs(title = "Distribution of Square Footage", x = "Square Footage", y = "Count")

# Scatter plot of Square Footage vs. Bedrooms
ggplot(house_data, aes(x = in.sqft, y = in.bedrooms)) +
  geom_point(aes(color = in.geometry_stories), size = 3) +
  labs(title = "Square Footage vs. Bedrooms by Number of Stories",
       x = "Square Footage", y = "Number of Bedrooms") +
  scale_color_gradient(low = "blue", high = "red")

# Bar plot of HVAC Cooling Types
ggplot(house_data, aes(x = in.hvac_cooling_type)) +
  geom_bar(fill = "steelblue") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Distribution of HVAC Cooling Types", x = "HVAC Cooling Type", y = "Count")

# Bar plot of HVAC Heating Types
ggplot(house_data, aes(x = in.hvac_heating_type)) +
  geom_bar(fill = "darkgreen") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(title = "Distribution of HVAC Heating Types", x = "HVAC Heating Type", y = "Count")

# Boxplot for HVAC Efficiency Ratings (Cooling)
ggplot(house_data, aes(x = in.hvac_cooling_efficiency, y = in.sqft)) +
  geom_boxplot(fill = "lightblue") +
  labs(title = "Cooling Efficiency Ratings vs. Square Footage", x = "Cooling Efficiency", y = "Square Footage")

# Boxplot for HVAC Efficiency Ratings (Heating)
ggplot(house_data, aes(x = in.hvac_heating_efficiency, y = in.sqft)) +
  geom_boxplot(fill = "lightgreen") +
  labs(title = "Heating Efficiency Ratings vs. Square Footage", x = "Heating Efficiency", y = "Square Footage")

# Save all plots to a PDF file
ggsave("house_data_eda.pdf")

```


```{r}
# Load necessary libraries
library(ggplot2)
library(readr)
library(dplyr)
library(lubridate)
library(openair)   # For wind rose plot

# Set the working directory to where your dataset is located
setwd("C:/Users/puroh/OneDrive/Documents/IDS/Static_House_data")

# Read the dataset
weather_data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Weather/weather_data_filtered.csv")

# Convert time column to POSIXct date-time format
weather_data$time <- ymd_hms(weather_data$time)

# Summary of the dataset
summary(weather_data)

colnames(weather_data)
# Time Series Plot for Temperature and Humidity
ggplot(weather_data, aes(x = time)) +
  geom_line(aes(y = `Dry Bulb Temperature [°C]`, colour = "Temperature")) +
  geom_line(aes(y = `Relative Humidity [%]`, colour = "Humidity")) +
  scale_colour_manual("", 
                      breaks = c("Temperature", "Humidity"),
                      values = c("red", "blue")) +
  labs(title = "Temperature and Humidity Over Time", x = "Time", y = "Measure") +
  theme_minimal()

# Wind Rose for Wind Direction and Speed
wind_rose_data <- weather_data %>%
  select(Wind_Speed = `Wind Speed [m/s]`, Wind_Direction = `Wind Direction [Deg]`)
windRose(wind_rose_data, ws = "Wind_Speed", wd = "Wind_Direction",
         main = "Wind Rose", speed.cuts = seq(0, 12, 2), angle = 30)



```

```{r}
library(dplyr)
library(readr)

# Load datasets
house_data_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Static_House_data/house_data_filtered.csv"
weather_data_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Weather/weather_data_filtered.csv"
energy_data_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Energy/energy_data_final.csv"

# Read the data from the CSV files
house_data <- read_csv(house_data_path)
weather_data <- read_csv(weather_data_path)
energy_data <- read_csv(energy_data_path)

# Merge Energy data with Weather data on the 'time' column
energy_weather_merged <- merge(energy_data, weather_data, by = "time", all = TRUE)

# Merge the above result with House data on the 'bldg_id' column
final_merged_data <- merge(energy_weather_merged, house_data, by = "bldg_id", all = TRUE)

# Optionally, inspect the first few rows of the merged dataset
print(head(final_merged_data))

colnames(final_merged_data)

# Save the final merged dataset
write_csv(final_merged_data, "C:/Users/puroh/OneDrive/Documents/IDS/Final/Merged_Dataset.csv")

# Print a confirmation message
print("All datasets have been successfully merged and saved.")

```
```{r}
# Load necessary library
library(readr)

# Read the dataset
dataset <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/Merged_Dataset.csv")

# Generate valid R names and assign them to the column names of the dataset
colnames(dataset) <- make.names(colnames(dataset), unique = TRUE)

# Print the new column names to verify
print(colnames(dataset))

# Optionally, you can write the modified dataset to a new CSV file
write_csv(dataset, "C:/Users/puroh/OneDrive/Documents/IDS/Final/Cleaned_Merged_Dataset.csv")

```
Step 2: Exploratory Data Analysis (EDA)

a. Energy consumption trends over the days of July.
b. The relationship between temperature, humidity, and energy usage.
c. HVAC system types and their impact on energy consumption.


```{r}


# Load the dataset
library(readr)
data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/Cleaned_Merged_Dataset.csv")
```


```{r}
# View the first few rows of the dataset
head(data)

# Summary of the dataset
summary(data)

# Structure of the dataset
str(data)
```

```{r}
# Check for NA values
sum(is.na(data))

# Optionally, remove rows with NA values if they are not numerous
# data <- na.omit(data)

```

```{r}
library(ggplot2)
library(dplyr)

# Summarizing total energy, heating, and cooling consumption
energy_summary <- data %>%
  group_by(time) %>%
  summarise(Total_Energy = sum(total_energy),
            Total_Heating = sum(Heating),
            Total_Cooling = sum(Cooling))

# Plotting total energy vs heating and cooling
ggplot(energy_summary, aes(x = time)) +
  geom_line(aes(y = Total_Heating, colour = "Heating")) +
  geom_line(aes(y = Total_Cooling, colour = "Cooling")) +
  labs(title = "Energy Consumption Over Time", x = "Time", y = "Energy (kWh)") +
  theme_minimal() +
  scale_color_manual(values = c("Heating" = "red", "Cooling" = "blue"))

```

```{r}
# Temperature effect on Heating and Cooling
ggplot(data, aes(x = Dry.Bulb.Temperature...C.)) +
  geom_smooth(aes(y = Heating, colour = "Heating"), method = "lm") +
  geom_smooth(aes(y = Cooling, colour = "Cooling"), method = "lm") +
  labs(title = "Effect of Temperature on Heating and Cooling", x = "Temperature (°C)", y = "Energy (kWh)") +
  scale_color_manual(values = c("Heating" = "red", "Cooling" = "blue"))

```


```{r}
library(ggplot2)
library(dplyr)

# Assuming data is already loaded and appropriate libraries are loaded
# Summarizing total energy by HVAC type for better visualization
data_grouped <- data %>%
  group_by(in.hvac_heating_type, in.hvac_cooling_type) %>%
  summarise(Total_Heating = sum(Heating), Total_Cooling = sum(Cooling), Total_Energy = sum(total_energy), .groups = 'drop')

# Horizontal Bar Plot for Heating by HVAC Heating Type
ggplot(data_grouped, aes(y = reorder(in.hvac_heating_type, Total_Heating), x = Total_Heating, fill = in.hvac_heating_type)) +
  geom_bar(stat = "identity") +
  facet_wrap(~in.hvac_cooling_type, scales = "free_y") +
  labs(title = "Total Heating by HVAC Heating Type", x = "Total Heating Energy (kWh)", y = "HVAC Heating Type") +
  theme_minimal() +
  theme(axis.text.y = element_text(angle = 0, hjust = 1))  # Adjust text angle for better legibility

# Horizontal Bar Plot for Cooling by HVAC Cooling Type
ggplot(data_grouped, aes(y = reorder(in.hvac_cooling_type, Total_Cooling), x = Total_Cooling, fill = in.hvac_cooling_type)) +
  geom_bar(stat = "identity") +
  facet_wrap(~in.hvac_heating_type, scales = "free_y") +
  labs(title = "Total Cooling by HVAC Cooling Type", x = "Total Cooling Energy (kWh)", y = "HVAC Cooling Type") +
  theme_minimal() +
  theme(axis.text.y = element_text(angle = 0, hjust = 1))  # Adjust text angle for better legibility

```



Step 3: Feature Engineering
Time Features: Hour of the day, day of the week (weekend vs. weekday), which can capture daily and weekly cycles in energy usage.
Weather Interactions: Interactions between temperature, humidity, and solar radiation that might affect energy needs.

Hourly Breakdowns: Identifies the hour of the day which could capture diurnal energy usage patterns.
Weekday vs. Weekend: Distinguishes between weekdays and weekends to capture potential variances in energy consumption patterns.
Temperature-Humidity Interaction: Reflects the combined effect of temperature and humidity, which may impact HVAC energy needs.
Temperature-Wind Speed Interaction: Accounts for the effect of wind cooling, potentially reducing cooling energy requirements.

```{r}
# Load necessary libraries
library(dplyr)
library(lubridate)

# Assuming your dataset is named 'data'
# Convert your time column to POSIXct if it's not already
data$time <- as.POSIXct(data$time, format = "%Y-%m-%d %H:%M:%S")

# Feature Engineering
data_feature <- data %>%
  mutate(
    # Hourly Breakdown
    Hour = hour(time),
    
    # Weekday vs. Weekend (1 for weekend, 0 for weekday)
    Weekend = ifelse(weekdays(time) %in% c("Saturday", "Sunday"), 1, 0),
    
    # Temperature-Humidity Interaction
    Temp_Humidity_Interaction = Dry.Bulb.Temperature...C. * Relative.Humidity....,
    
    # Temperature-Wind Speed Interaction
    Temp_WindSpeed_Interaction = Dry.Bulb.Temperature...C. * Wind.Speed..m.s.
  )

# Viewing the first few rows to confirm new features
head(data_feature)

```

```{r}
library(ggplot2)

# Hourly energy consumption pattern
ggplot(data_feature, aes(x = Hour, y = total_energy)) +
  geom_line(stat = "summary", fun = "mean") +
  labs(title = "Average Hourly Energy Consumption",
       x = "Hour of the Day",
       y = "Average Energy Consumption (kWh)") +
  theme_minimal()

```

```{r}
# Weekday vs. Weekend energy consumption
ggplot(data_feature, aes(x = as.factor(Weekend), y = total_energy)) +
  geom_boxplot() +
  scale_x_discrete(labels = c("0" = "Weekday", "1" = "Weekend")) +
  labs(title = "Energy Consumption: Weekday vs Weekend",
       x = "",
       y = "Energy Consumption (kWh)") +
  theme_minimal()

```

```{r}
# Temperature-Humidity Interaction
ggplot(data_feature, aes(x = Temp_Humidity_Interaction, y = total_energy)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "blue", se = FALSE) +
  labs(title = "Energy Consumption vs Temperature-Humidity Interaction",
       x = "Temperature-Humidity Interaction",
       y = "Total Energy Consumption (kWh)") +
  theme_minimal()

```

```{r}
# Temperature-Wind Speed Interaction
ggplot(data_feature, aes(x = Temp_WindSpeed_Interaction, y = total_energy)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(title = "Energy Consumption vs Temperature-Wind Speed Interaction",
       x = "Temperature-Wind Speed Interaction",
       y = "Total Energy Consumption (kWh)") +
  theme_minimal()

```

```{r}
# Load the necessary libraries
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)

# Load the dataset
data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/Cleaned_Merged_Dataset.csv")

colnames(data)

# Convert the 'time' column to a datetime format, if it's not already
data$time <- as.POSIXct(data$time, format = "%Y-%m-%d %H:%M:%S")

# Ensure that HVAC types are factors
data$in.hvac_cooling_type <- as.factor(data$in.hvac_cooling_type)
data$in.hvac_heating_type <- as.factor(data$in.hvac_heating_type)

# Create a new column 'Month' to filter by
data <- data %>%
  mutate(Month = month(time))

# Splitting the dataset
train_data <- data %>% filter(Month != 7)
test_data <- data %>% filter(Month == 7)

# Building the model for Heating
model_heating <- lm(Heating ~ time + electricity + fuel + natural_gas + propane + 
                      Dry.Bulb.Temperature...C. + Relative.Humidity.... + Wind.Speed..m.s. +
                      in.sqft + in.bedrooms + in.geometry_stories + in.hvac_cooling_type +
                      in.hvac_heating_type + in.hvac_heating_efficiency + 
                      in.hvac_cooling_efficiency + in.hvac_has_ducts + in.occupants, data = train_data)

# Building the model for Cooling
model_cooling <- lm(Cooling ~ time + electricity + fuel + natural_gas + propane + 
                      Dry.Bulb.Temperature...C. + Relative.Humidity.... + Wind.Speed..m.s. +
                      in.sqft + in.bedrooms + in.geometry_stories + in.hvac_cooling_type +
                      in.hvac_heating_type + in.hvac_heating_efficiency + 
                      in.hvac_cooling_efficiency + in.hvac_has_ducts + in.occupants, data = train_data)

# Making predictions for the test set (July)
test_data$predicted_heating <- predict(model_heating, newdata = test_data)
test_data$predicted_cooling <- predict(model_cooling, newdata = test_data)

# Visualization for Heating
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = Heating), color = 'blue') +
  geom_line(aes(y = predicted_heating), color = 'red') +
  labs(title = "Actual vs Predicted Heating Energy Consumption for July",
       x = "Time",
       y = "Energy Consumption (kWh)") +
  theme_minimal()

# Visualization for Cooling
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = Cooling), color = 'green') +
  geom_line(aes(y = predicted_cooling), color = 'orange') +
  labs(title = "Actual vs Predicted Cooling Energy Consumption for July",
       x = "Time",
       y = "Energy Consumption (kWh)") +
  theme_minimal()

# Create a dataframe with actual and predicted values for July
july_comparison <- test_data %>%
  select(time, Heating, predicted_heating, Cooling, predicted_cooling)

# Display the dataframe
print(july_comparison)

```

```{r}
# Load the necessary library for metrics
library(Metrics)

# Actual vs Predicted for Heating
actual_heating <- test_data$Heating
predicted_heating <- test_data$predicted_heating

# Metrics for Heating Model
mse_heating <- mse(actual_heating, predicted_heating)
rmse_heating <- sqrt(mse_heating)
mae_heating <- mae(actual_heating, predicted_heating)
r2_heating <- cor(actual_heating, predicted_heating)^2

# Print Heating Model Metrics
cat("Heating Model Metrics:\n")
cat("MSE:", mse_heating, "\n")
cat("RMSE:", rmse_heating, "\n")
cat("MAE:", mae_heating, "\n")
cat("R-squared:", r2_heating, "\n\n")

# Actual vs Predicted for Cooling
actual_cooling <- test_data$Cooling
predicted_cooling <- test_data$predicted_cooling

# Metrics for Cooling Model
mse_cooling <- mse(actual_cooling, predicted_cooling)
rmse_cooling <- sqrt(mse_cooling)
mae_cooling <- mae(actual_cooling, predicted_cooling)
r2_cooling <- cor(actual_cooling, predicted_cooling)^2

# Print Cooling Model Metrics
cat("Cooling Model Metrics:\n")
cat("MSE:", mse_cooling, "\n")
cat("RMSE:", rmse_cooling, "\n")
cat("MAE:", mae_cooling, "\n")
cat("R-squared:", r2_cooling, "\n")

```
```{r}
# Load the necessary libraries
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(Metrics)

# Load the dataset
data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/Cleaned_Merged_Dataset.csv")

# Convert the 'time' column to a datetime format
data$time <- as.POSIXct(data$time, format = "%Y-%m-%d %H:%M:%S")

# Ensure that HVAC types and other categorical variables are factors
data$in.hvac_cooling_type <- as.factor(data$in.hvac_cooling_type)
data$in.hvac_heating_type <- as.factor(data$in.hvac_heating_type)
data$in.hvac_has_ducts <- as.factor(data$in.hvac_has_ducts)

# Check each factor variable to make sure it has more than one level
factor_vars <- c("in.hvac_cooling_type", "in.hvac_heating_type", "in.hvac_has_ducts")

# Print the number of levels for each factor
for (var in factor_vars) {
  cat(var, "levels:", nlevels(data[[var]]), "\n")
}

# Filter out factor variables with just one level from the model
factor_vars_to_keep <- factor_vars[sapply(data[factor_vars], nlevels) > 1]
formula_vars <- c("time", "Heating", "Cooling", "Dry.Bulb.Temperature...C.", "Relative.Humidity....",
                  "Wind.Speed..m.s.", "Global.Horizontal.Radiation..W.m2.", "Direct.Normal.Radiation..W.m2.",
                  "Diffuse.Horizontal.Radiation..W.m2.", "in.sqft", "in.bedrooms", "in.geometry_stories",
                  "in.hvac_heating_efficiency", "in.hvac_cooling_efficiency", "in.hvac_has_ducts")

# Add the selected factor variables to the formula variables
formula_vars <- c(formula_vars, factor_vars_to_keep)

# Create the regression formula for total_energy
regression_formula_total_energy <- as.formula(paste("total_energy ~", paste(formula_vars, collapse = " + ")))

# Create a new column 'Month' to filter by
data <- data %>%
  mutate(Month = month(time))

# Split the dataset into train and test (July)
train_data <- data %>% filter(Month != 7)
test_data <- data %>% filter(Month == 7)

# Build the model using the train_data
model_total_energy <- lm(regression_formula_total_energy, data = train_data)

# Make predictions on the test_data
test_data$predicted_total_energy <- predict(model_total_energy, newdata = test_data)

# Visualization for Total Energy
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = total_energy), color = 'blue') +
  geom_line(aes(y = predicted_total_energy), color = 'red') +
  labs(title = "Actual vs Predicted Total Energy Consumption for July",
       x = "Time", y = "Total Energy (kWh)") +
  theme_minimal()

# Metrics calculation for Total Energy
actual_total_energy <- test_data$total_energy
predicted_total_energy <- test_data$predicted_total_energy
mse_total_energy <- mse(actual_total_energy, predicted_total_energy)
rmse_total_energy <- sqrt(mse_total_energy)
mae_total_energy <- mae(actual_total_energy, predicted_total_energy)
r2_total_energy <- cor(actual_total_energy, predicted_total_energy)^2

# Output the metrics
cat("Total Energy Model Metrics for July:\n")
cat("MSE:", mse_total_energy, "\n")
cat("RMSE:", rmse_total_energy, "\n")
cat("MAE:", mae_total_energy, "\n")
cat("R-squared:", r2_total_energy, "\n")

# Create and display a dataframe with actual and predicted values for July
july_comparison <- test_data %>%
  select(time, total_energy, predicted_total_energy)
print(july_comparison)

```

```{r}
  # Adjust the temperature in the July test dataset by 5 degrees
test_data_increased_temp <- test_data %>%
  mutate(`Dry.Bulb.Temperature...C.` = `Dry.Bulb.Temperature...C.` + 5)

# Use the existing models to predict with the new test data
test_data_increased_temp$predicted_heating <- predict(model_heating, newdata = test_data_increased_temp)
test_data_increased_temp$predicted_cooling <- predict(model_cooling, newdata = test_data_increased_temp)

# Save the new weather test data for July with increased temperature to CSV
write_csv(test_data_increased_temp, "C:/Users/puroh/OneDrive/Documents/IDS/Final/test_july_increased.csv")

# Print a message that the file has been saved
cat("The new weather test data for July with increased temperature has been saved at C:/Users/puroh/OneDrive/Documents/IDS/Final/test_july_increased.csv")

```

```{r}
# Load the necessary libraries
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(Metrics)

# Load the training dataset
train_data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/Cleaned_Merged_Dataset.csv")

# Convert the 'time' column to a datetime format
train_data$time <- as.POSIXct(train_data$time, format = "%Y-%m-%d %H:%M:%S")

# Ensure that HVAC types and other categorical variables are factors
train_data$in.hvac_cooling_type <- as.factor(train_data$in.hvac_cooling_type)
train_data$in.hvac_heating_type <- as.factor(train_data$in.hvac_heating_type)
train_data$in.hvac_has_ducts <- as.factor(train_data$in.hvac_has_ducts)

# Check each factor variable to make sure it has more than one level
factor_vars <- c("in.hvac_cooling_type", "in.hvac_heating_type", "in.hvac_has_ducts")

# Print the number of levels for each factor
for (var in factor_vars) {
  cat(var, "levels:", nlevels(train_data[[var]]), "\n")
}

# Filter out factor variables with just one level from the model
factor_vars_to_keep <- factor_vars[sapply(train_data[factor_vars], nlevels) > 1]
formula_vars <- c("time", "electricity", "fuel", "natural_gas", "propane", "total_energy", 
                  "Dry.Bulb.Temperature...C.", "Relative.Humidity....", "Wind.Speed..m.s.",
                  "in.sqft", "in.bedrooms", "in.geometry_stories", "in.hvac_heating_efficiency",
                  "in.hvac_cooling_efficiency", "in.occupants")
formula_vars <- c(formula_vars, factor_vars_to_keep)

# Create the regression formula
regression_formula_heating <- as.formula(paste("Heating ~", paste(formula_vars, collapse = " + ")))
regression_formula_cooling <- as.formula(paste("Cooling ~", paste(formula_vars, collapse = " + ")))

# Split the training dataset (excluding July)
train_data <- train_data %>% 
  mutate(Month = month(time)) %>%
  filter(Month != 7)

# Load the new test dataset for July with the increased temperature
test_data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/test_july_increased.csv")
test_data$time <- as.POSIXct(test_data$time, format = "%Y-%m-%d %H:%M:%S")
test_data$`Dry.Bulb.Temperature...C.` <- test_data$`Dry.Bulb.Temperature...C.` + 5

# Ensure consistency of factor levels between train and test data
for (var in factor_vars_to_keep) {
  levels(test_data[[var]]) <- levels(train_data[[var]])
}

# Build the models using the train_data
model_heating <- lm(regression_formula_heating, data = train_data)
model_cooling <- lm(regression_formula_cooling, data = train_data)

# Make predictions on the test_data
test_data$predicted_heating <- predict(model_heating, newdata = test_data)
test_data$predicted_cooling <- predict(model_cooling, newdata = test_data)

# Visualization
# Visualization for Heating
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = Heating), color = 'blue') +
  geom_line(aes(y = predicted_heating), color = 'red') +
  labs(title = "Actual vs Predicted Heating Energy Consumption for July",
       x = "Time",
       y = "Energy Consumption (kWh)") +
  theme_minimal()

# Visualization for Cooling
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = Cooling), color = 'green') +
  geom_line(aes(y = predicted_cooling), color = 'orange') +
  labs(title = "Actual vs Predicted Cooling Energy Consumption for July",
       x = "Time",
       y = "Energy Consumption (kWh)") +
  theme_minimal()

# Metrics calculation for heating
actual_heating <- test_data$Heating
predicted_heating <- test_data$predicted_heating
mse_heating <- mse(actual_heating, predicted_heating)
rmse_heating <- sqrt(mse_heating)
mae_heating <- mae(actual_heating, predicted_heating)
r2_heating <- cor(actual_heating, predicted_heating)^2

# Metrics calculation for cooling
actual_cooling <- test_data$Cooling
predicted_cooling <- test_data$predicted_cooling
mse_cooling <- mse(actual_cooling, predicted_cooling)
rmse_cooling <- sqrt(mse_cooling)
mae_cooling <- mae(actual_cooling, predicted_cooling)
r2_cooling <- cor(actual_cooling, predicted_cooling)^2

# Output the metrics
cat("Heating Model Metrics with Increased Temperature:\n")
cat("MSE:", mse_heating, "\n")
cat("RMSE:", rmse_heating, "\n")
cat("MAE:", mae_heating, "\n")
cat("R-squared:", r2_heating, "\n\n")

cat("Cooling Model Metrics with Increased Temperature:\n")
cat("MSE:", mse_cooling, "\n")
cat("RMSE:", rmse_cooling, "\n")
cat("MAE:", mae_cooling, "\n")
cat("R-squared:", r2_cooling, "\n")

# Create and display a dataframe with actual and predicted values for July
july_comparison <- test_data %>%
  select(time, Heating, predicted_heating, Cooling, predicted_cooling)
print(july_comparison)

```


```{r}
# Load the necessary libraries
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(Metrics)

# Load the training dataset
train_data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/Cleaned_Merged_Dataset.csv")

# Convert the 'time' column to a datetime format
train_data$time <- as.POSIXct(train_data$time, format = "%Y-%m-%d %H:%M:%S")

# Ensure that HVAC types and other categorical variables are factors
train_data$in.hvac_cooling_type <- as.factor(train_data$in.hvac_cooling_type)
train_data$in.hvac_heating_type <- as.factor(train_data$in.hvac_heating_type)
train_data$in.hvac_has_ducts <- as.factor(train_data$in.hvac_has_ducts)

# Check each factor variable to make sure it has more than one level
factor_vars <- c("in.hvac_cooling_type", "in.hvac_heating_type", "in.hvac_has_ducts")

# Print the number of levels for each factor
for (var in factor_vars) {
  cat(var, "levels:", nlevels(train_data[[var]]), "\n")
}

# Filter out factor variables with just one level from the model
factor_vars_to_keep <- factor_vars[sapply(train_data[factor_vars], nlevels) > 1]
formula_vars <- c("time", "Heating", "Cooling", "Dry.Bulb.Temperature...C.", "Relative.Humidity....",
                  "Wind.Speed..m.s.", "Global.Horizontal.Radiation..W.m2.", "Direct.Normal.Radiation..W.m2.",
                  "Diffuse.Horizontal.Radiation..W.m2.", "in.sqft", "in.bedrooms", "in.geometry_stories",
                  "in.hvac_heating_efficiency", "in.hvac_cooling_efficiency", "in.hvac_has_ducts")

# Add the selected factor variables to the formula variables
formula_vars <- c(formula_vars, factor_vars_to_keep)

# Create the regression formula for total_energy
regression_formula_total_energy <- as.formula(paste("total_energy ~", paste(formula_vars, collapse = " + ")))

# Split the training dataset
train_data <- train_data %>% 
  mutate(Month = month(time)) %>%
  filter(Month != 7)

# Load the new test dataset for July with the increased temperature
test_data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/test_july_increased.csv")
test_data$time <- as.POSIXct(test_data$time, format = "%Y-%m-%d %H:%M:%S")

# Ensure consistency of factor levels between train and test data
for (var in factor_vars_to_keep) {
  levels(test_data[[var]]) <- levels(train_data[[var]])
}

# Build the model using the train_data
model_total_energy <- lm(regression_formula_total_energy, data = train_data)

# Make predictions on the test_data
test_data$predicted_total_energy <- predict(model_total_energy, newdata = test_data)

# Visualization for Total Energy
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = total_energy), color = 'blue') +
  geom_line(aes(y = predicted_total_energy), color = 'red') +
  labs(title = "Actual vs Predicted Total Energy Consumption for July",
       x = "Time", y = "Total Energy (kWh)") +
  theme_minimal()

# Metrics calculation for Total Energy
actual_total_energy <- test_data$total_energy
predicted_total_energy <- test_data$predicted_total_energy
mse_total_energy <- mse(actual_total_energy, predicted_total_energy)
rmse_total_energy <- sqrt(mse_total_energy)
mae_total_energy <- mae(actual_total_energy, predicted_total_energy)
r2_total_energy <- cor(actual_total_energy, predicted_total_energy)^2

# Output the metrics
cat("Total Energy Model Metrics with Increased Temperature:\n")
cat("MSE:", mse_total_energy, "\n")
cat("RMSE:", rmse_total_energy, "\n")
cat("MAE:", mae_total_energy, "\n")
cat("R-squared:", r2_total_energy, "\n")

# Create and display a dataframe with actual and predicted values for July
july_comparison <- test_data %>%
  select(time, total_energy, predicted_total_energy)
print(july_comparison)

```

```{r}
# Visualization for Predicted Total Energy with Peak Highlight
ggplot(test_data, aes(x = time, y = predicted_total_energy)) +
  geom_line(color = 'blue') +
  geom_point(data = test_data %>% filter(predicted_total_energy == max(predicted_total_energy)), aes(color = "Peak Energy"), size = 3) +
  labs(title = "Predicted Total Energy Consumption for July",
       x = "Time", y = "Predicted Total Energy (kWh)") +
  scale_color_manual(values = c("Peak Energy" = "red", "Other" = "black")) +
  theme_minimal()

# Find the date and time with the highest predicted total energy consumed
peak_time <- test_data %>%
  filter(predicted_total_energy == max(predicted_total_energy)) %>%
  select(time, predicted_total_energy)

cat("Date and Time with the Highest Predicted Total Energy Consumption:\n")
print(peak_time)


```



```{r}
# Load the necessary libraries
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(xgboost)
library(caret)  # for data scaling

# Load the dataset
data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/Cleaned_Merged_Dataset.csv")

# Convert the 'time' column to a datetime format
data$time <- as.POSIXct(data$time, format = "%Y-%m-%d %H:%M:%S")

# Explicitly convert all categorical variables to numeric
categorical_vars <- c("in.hvac_cooling_type", "in.hvac_heating_type", "in.hvac_has_ducts")
data[categorical_vars] <- lapply(data[categorical_vars], function(x) as.numeric(as.factor(x)))

# Create a new column 'Month' to filter by
data <- mutate(data, Month = month(time))

# Splitting the dataset
train_data <- filter(data, Month != 7)
test_data <- filter(data, Month == 7)

# Identifying numeric variables for scaling
numeric_vars <- setdiff(names(train_data), c("time", "Month", "Heating", "Cooling"))
# Ensure all variables are indeed numeric
train_data[numeric_vars] <- sapply(train_data[numeric_vars], as.numeric)
test_data[numeric_vars] <- sapply(test_data[numeric_vars], as.numeric)

# Scaling the data
pre_proc_values <- preProcess(train_data[, numeric_vars, drop = FALSE], method = c("center", "scale"))
train_data_scaled <- predict(pre_proc_values, train_data[, numeric_vars, drop = FALSE])
test_data_scaled <- predict(pre_proc_values, test_data[, numeric_vars, drop = FALSE])

# Reattach the non-scaled and non-numeric data
train_data_final <- bind_cols(train_data_scaled, select(train_data, time, Heating, Cooling))
test_data_final <- bind_cols(test_data_scaled, select(test_data, time, Heating, Cooling))

# Convert all factor columns to numeric explicitly for safety
train_data_final <- data.frame(lapply(train_data_final, function(x) if(is.factor(x)) as.numeric(as.character(x)) else x))
test_data_final <- data.frame(lapply(test_data_final, function(x) if(is.factor(x)) as.numeric(as.character(x)) else x))

# Prepare matrices for xgboost
dtrain_heating <- xgb.DMatrix(data = as.matrix(select(train_data_final, -c(time, Heating, Cooling))), label = train_data_final$Heating)
dtrain_cooling <- xgb.DMatrix(data = as.matrix(select(train_data_final, -c(time, Heating, Cooling))), label = train_data_final$Cooling)
dtest <- xgb.DMatrix(data = as.matrix(select(test_data_final, -c(time, Heating, Cooling))))

# Train the model
param <- list(max_depth = 3, eta = 0.1, silent = 1, objective = "reg:squarederror", nthread = 2)
nrounds <- 100

model_xgb_heating <- xgb.train(params = param, data = dtrain_heating, nrounds = nrounds)
model_xgb_cooling <- xgb.train(params = param, data = dtrain_cooling, nrounds = nrounds)

# Make predictions for the test set (July)
test_data_final$predicted_heating <- predict(model_xgb_heating, dtest)
test_data_final$predicted_cooling <- predict(model_xgb_cooling, dtest)

# Visualization for Heating
ggplot(test_data_final, aes(x = time)) +
  geom_line(aes(y = Heating), color = 'blue') +
  geom_line(aes(y = predicted_heating), color = 'red', linetype = "dashed") +
  labs(title = "Actual vs Predicted Heating Energy Consumption for July",
       x = "Time", y = "Energy Consumption (kWh)") +
  theme_minimal()

# Visualization for Cooling
ggplot(test_data_final, aes(x = time)) +
  geom_line(aes(y = Cooling), color = 'green') +
  geom_line(aes(y = predicted_cooling), color = 'orange', linetype = "dashed") +
  labs(title = "Actual vs Predicted Cooling Energy Consumption for July",
       x = "Time", y = "Energy Consumption (kWh)") +
  theme_minimal()

# Calculate metrics
actual_heating <- test_data_final$Heating
predicted_heating <- test_data_final$predicted_heating
mse_heating <- mean((predicted_heating - actual_heating)^2)
rmse_heating <- sqrt(mse_heating)
mae_heating <- mean(abs(predicted_heating - actual_heating))
r2_heating <- cor(actual_heating, predicted_heating)^2

actual_cooling <- test_data_final$Cooling
predicted_cooling <- test_data_final$predicted_cooling
mse_cooling <- mean((predicted_cooling - actual_cooling)^2)
rmse_cooling <- sqrt(mse_cooling)
mae_cooling <- mean(abs(predicted_cooling - actual_cooling))
r2_cooling <- cor(actual_cooling, predicted_cooling)^2

# Print metrics
cat("Heating Model Metrics:\n")
cat("MSE:", mse_heating, "\n")
cat("RMSE:", rmse_heating, "\n")
cat("MAE:", mae_heating, "\n")
cat("R-squared:", r2_heating, "\n\n")

cat("Cooling Model Metrics:\n")
cat("MSE:", mse_cooling, "\n")
cat("RMSE:", rmse_cooling, "\n")
cat("MAE:", mae_cooling, "\n")
cat("R-squared:", r2_cooling, "\n")

# Create and display a dataframe with actual and predicted values for July
july_comparison <- select(test_data_final, time, Heating, predicted_heating, Cooling, predicted_cooling)
print(july_comparison)

```



```{r}
# Load the necessary libraries
library(readr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(xgboost)
library(Metrics)

# Load the training dataset
train_data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/Cleaned_Merged_Dataset.csv")

# Convert the 'time' column to a datetime format
train_data$time <- as.POSIXct(train_data$time, format = "%Y-%m-%d %H:%M:%S")

# Ensure that HVAC types and other categorical variables are factors
train_data$in.hvac_cooling_type <- as.factor(train_data$in.hvac_cooling_type)
train_data$in.hvac_heating_type <- as.factor(train_data$in.hvac_heating_type)
train_data$in.hvac_has_ducts <- as.factor(train_data$in.hvac_has_ducts)

# Create a 'Month' column to filter the data
train_data <- train_data %>%
  mutate(Month = month(time)) %>%
  select(-Month)  # Remove Month from data to avoid leakage

# Load the new test dataset for July with the increased temperature
test_data <- read_csv("C:/Users/puroh/OneDrive/Documents/IDS/Final/test_july_increased.csv")
test_data$time <- as.POSIXct(test_data$time, format = "%Y-%m-%d %H:%M:%S")
test_data$`Dry.Bulb.Temperature...C.` <- test_data$`Dry.Bulb.Temperature...C.` + 5

# Convert test data factors using train data's levels to ensure consistency
test_data$in.hvac_cooling_type <- factor(test_data$in.hvac_cooling_type, levels = levels(train_data$in.hvac_cooling_type))
test_data$in.hvac_heating_type <- factor(test_data$in.hvac_heating_type, levels = levels(train_data$in.hvac_heating_type))
test_data$in.hvac_has_ducts <- factor(test_data$in.hvac_has_ducts, levels = levels(train_data$in.hvac_has_ducts))

# Check for any factor with only one level and remove such factors from the model
factor_vars <- c("in.hvac_cooling_type", "in.hvac_heating_type", "in.hvac_has_ducts")
factor_vars_to_keep <- sapply(factor_vars, function(var) {
  if (nlevels(factor(train_data[[var]])) > 1) return(var)
  else {
    train_data[[var]] <- NULL  # remove factors with one level from train_data
    test_data[[var]] <- NULL  # remove factors with one level from test_data
    NULL  # do not keep this factor in the model
  }
})

# Create the regression formulas
formula_vars <- c("time", "electricity", "fuel", "natural_gas", "propane", "total_energy", 
                  "Dry.Bulb.Temperature...C.", "Relative.Humidity....", "Wind.Speed..m.s.",
                  "in.sqft", "in.bedrooms", "in.geometry_stories", "in.hvac_heating_efficiency",
                  "in.hvac_cooling_efficiency", "in.occupants", factor_vars_to_keep)

regression_formula_heating <- as.formula(paste("Heating ~", paste(formula_vars, collapse = " + ")))
regression_formula_cooling <- as.formula(paste("Cooling ~", paste(formula_vars, collapse = " + ")))

# Build the models using the train_data
model_heating <- lm(regression_formula_heating, data = train_data)
model_cooling <- lm(regression_formula_cooling, data = train_data)

# Make predictions on the test_data
test_data$predicted_heating <- predict(model_heating, newdata = test_data)
test_data$predicted_cooling <- predict(model_cooling, newdata = test_data)

# Visualization for Heating
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = Heating), color = 'blue') +
  geom_line(aes(y = predicted_heating), color = 'red', linetype = "dashed") +
  labs(title = "Actual vs Predicted Heating Energy Consumption for July",
       x = "Time", y = "Energy Consumption (kWh)") +
  theme_minimal()

# Visualization for Cooling
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = Cooling), color = 'green') +
  geom_line(aes(y = predicted_cooling), color = 'orange', linetype = "dashed") +
  labs(title = "Actual vs Predicted Cooling Energy Consumption for July",
       x = "Time", y = "Energy Consumption (kWh)") +
  theme_minimal()

# Calculate metrics
actual_heating <- test_data$Heating
predicted_heating <- test_data$predicted_heating
mse_heating <- mse(actual_heating, predicted_heating)
rmse_heating <- sqrt(mse_heating)
mae_heating <- mae(actual_heating, predicted_heating)
r2_heating <- cor(actual_heating, predicted_heating)^2

actual_cooling <- test_data$Cooling
predicted_cooling <- test_data$predicted_cooling
mse_cooling <- mse(actual_cooling, predicted_cooling)
rmse_cooling <- sqrt(mse_cooling)
mae_cooling <- mae(actual_cooling, predicted_cooling)
r2_cooling <- cor(actual_cooling, predicted_cooling)^2

# Output the metrics
cat("Heating Model Metrics:\n")
cat("MSE:", mse_heating, "\n")
cat("RMSE:", rmse_heating, "\n")
cat("MAE:", mae_heating, "\n")
cat("R-squared:", r2_heating, "\n\n")

cat("Cooling Model Metrics:\n")
cat("MSE:", mse_cooling, "\n")
cat("RMSE:", rmse_cooling, "\n")
cat("MAE:", mae_cooling, "\n")
cat("R-squared:", r2_cooling, "\n")

# Create and display a dataframe with actual and predicted values for July
july_comparison <- select(test_data, time, Heating, predicted_heating, Cooling, predicted_cooling)
print(july_comparison)

```


```{r}
# Visualization for Predicted Heating Energy
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = Heating), color = 'blue') +
  geom_line(aes(y = predicted_heating), color = 'red', linetype = "dashed") +
  labs(title = "Actual vs Predicted Heating Energy Consumption for July",
       x = "Time", y = "Energy Consumption (kWh)") +
  theme_minimal()

# Visualization for Predicted Cooling Energy
ggplot(test_data, aes(x = time)) +
  geom_line(aes(y = Cooling), color = 'green') +
  geom_line(aes(y = predicted_cooling), color = 'orange', linetype = "dashed") +
  labs(title = "Actual vs Predicted Cooling Energy Consumption for July",
       x = "Time", y = "Energy Consumption (kWh)") +
  theme_minimal()

# Find the peak predicted heating energy consumed with the date
peak_heating_time <- test_data %>%
  filter(predicted_heating == max(predicted_heating)) %>%
  select(time, predicted_heating)

cat("Date and Time with the Highest Predicted Heating Energy Consumption:\n")
print(peak_heating_time)

# Find the peak predicted cooling energy consumed with the date
peak_cooling_time <- test_data %>%
  filter(predicted_cooling == max(predicted_cooling)) %>%
  select(time, predicted_cooling)

cat("Date and Time with the Highest Predicted Cooling Energy Consumption:\n")
print(peak_cooling_time)

#temperature 33.3 for date 2018-07-04 09:00:00

#temperature 36.7 for date 2018-07-23 15:00:00

```


```{r}
# Load the necessary library
library(readr)

# Define the paths to the datasets
train_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Final/train.csv"
test_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Final/test_july_increased.csv"

# Load the datasets
train_data <- read_csv(train_path)
test_data <- read_csv(test_path)

# Merge the datasets
combined_data <- bind_rows(train_data, test_data)

# Save the combined dataset to the same location
write_csv(combined_data, "C:/Users/puroh/OneDrive/Documents/IDS/Final/combined_dataset.csv")

# Output to confirm the save
cat("Combined dataset saved at 'C:/Users/puroh/OneDrive/Documents/IDS/Final/combined_dataset.csv'\n")

```

```{r}
# Load the necessary libraries
library(readr)
library(ggplot2)
library(lubridate)

# Load the combined dataset
combined_data_path <- "C:/Users/puroh/OneDrive/Documents/IDS/Final/combined_dataset.csv"
combined_data <- read_csv(combined_data_path)

# Convert the 'time' column to a datetime format, if it's not already
combined_data$time <- as.POSIXct(combined_data$time, format = "%Y-%m-%d %H:%M:%S")

# Create a ggplot to visualize total_energy vs time
ggplot(combined_data, aes(x = time, y = total_energy)) +
  geom_line() +  # Using a line plot
  labs(title = "Total Energy Consumption Over Time",
       x = "Time",
       y = "Total Energy (kWh)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Improve x-axis label readability

# Optionally, save the plot
ggsave("C:/Users/puroh/OneDrive/Documents/IDS/Final/energy_time_plot.png", width = 10, height = 6)

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

